---
title: "Data607 Assignment 3"
author: "Deepa"
date: "2/17/2022"
output: html_document
---



```{r}
library(tidyverse)
library(stringr)

```

## Question 1
Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"


 provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}
collegeMajor <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv", header = TRUE)

collegeMajor$Major %>% str_subset("DATA|STATISTICS")

```

## Questions 2

Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"
Into a format like this:


```{r}
vec.text = c('[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"')
```



```{r}
vec.text.char = gsub("(\\n\\[\\d+\\])|(^\\[\\d+\\])", "", vec.text)
vec.text.char = strsplit(vec.text.char, '\\"')
vec.text.char = unlist(vec.text.char)
vec.text.char = vec.text.char[grep("[a-z]", vec.text.char)]
vec.text.char
```

## Question3: The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

* Describe, in words, what these expressions will match:
    + "(.)\\1\\1"
    + "(.)(.)\\2\\1"
    + "(..)\1"
    + "(.).\\1.\\1"
    + "(.)(.)(.).*\\3\\2\\1"

 
## Answer3A: one chracter repeated three times in  a row


```{r }
x1<- "zzz"
str_detect(x1,"(.)\\1\\1")
```

## Answer3B: One character appears, followed by a second character twice, followed by first character
```{r}
x1<- "peep"
str_detect(x1,"(.)(.)\\2\\1")
```

## Answer3C:

Two character repeated one time 

```{r}
x1<- "soso"
str_detect(x1,"(..)\\1")
```

## Answer3D: First character, followed by any character followed by the first character, followed by any character, and then the first character again.

```{r}
x1<- "gpgeg"
str_detect(x1,"(.).\\1.\\1")
```

## Answer3E:
* The string must have three of any character, with any other characters afterwards as long as it ends with the original 3 backwards.
  Example
  + mopepom
  + moppom
  + mopecpom

```{r}
x1<- "moppom"
str_detect(x1,"(.)(.)(.).*\\3\\2\\1")

```

## Construct regular expressions to match words that:

## 1. Start and end with the same character

```{r}
str_view("pump", "^(.).*\\1$", match = T)
```

## 2. Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)

```{r}
str_view("salsa", "(..).*\\1", match = T)
```

## 3. Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

```{r}
str_view("settlements", "(.).*\\1.*\\1", match = T)
```




