---
title: "Data 607 week 9"
author: "Deepa Shama"
date: "4/1/2022"
output: html_document
---

## Week 9 Assignment – Web APIs (30 points)
Preparing Data (25 points)
Choose one of the New York Times APIs, request API key (1 point)
Construct an interface in R to read in the JSON data (14 points)
Transform data to an R dataframe (10 points)

Reproducibility (2 points)
Using R Markdown text and headers (2 points)
Workflow (2 points)
Included a brief description of the assigned problem.
Included an overview of your approach. Explained your reasoning.
Provided a conclusion (including any findings and recommendations).
Submission (1 points)
Published to rpubs and provided a link in your assignment submission.
Published to GitHub and provided a link in your assignment submission


## NY Times Web API

## Introduction:
In this assignment we are ask to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R Dataframe.To do this I use NYT developer API link  https://developer.nytimes.com/apis and then sign up for my own API key. I selected most popular new York Times article  API for for this assignment.
Here is MY API Key: xVAwOUxWWObztqjKP4SE1i11AuG1Gb57 


* Load Library:
  - httr:First I will load httr for getting data from API
  - jsonlite: use for parsing result
  - dplyr: use for pipe function

```{r}
library(httr)
library(jsonlite)
library(dplyr)

```


## Accessing data from web API using GET function


```{r}
my_url<- paste0("https://api.nytimes.com/svc/mostpopular/v2/shared/1/facebook.json?api-key=xVAwOUxWWObztqjKP4SE1i11AuG1Gb57")
my_raw_result<-httr::GET(my_url)
str(my_raw_result)
str(my_raw_result$content)
```

## Here I use httr as = text to convert raw to usable format with the content function

```{r}
my_content<-httr::content(my_raw_result, as= 'text')
str(my_content)
```

## I used jsonlite package is a JSON to parse the result. Its main strength is that it implements a bidirectional mapping between JSON data and the most important R data types.

```{r}
my_content_from_json<-jsonlite::fromJSON(my_content)
dplyr::glimpse(my_content_from_json)
```

## We will as.data.frame function to pulled data to convert into a dataframe

```{r}
df_json <- as.data.frame(my_content_from_json)
View(df_json)

```

 ## I Use colnames function to see all the columns 

```{r}
colnames(df_json)
```

## View url for the most viewed articles

```{r}
df_json %>%
    select(results.url)

```
## View results.published_date for the most viewed articles

```{r}
df_json %>%
    select(results.published_date)

```
## View results.section for the most viewed articles

```{r}
df_json %>%
    select(results.section)

```

## Conclusion:

This is my first time playing with web API and converting into a dataframe in R. I found GET function is a simpler way to load Web API in R.However, I had some challenges with raw data converting into most usable form of R. Then I use httr as = text to convert raw to usable format with the content function. I used jsonlite package for JSON to parse the result. Its main strength is that it implements a bidirectional mapping between JSON data and the most important R data types.


### References:
 + https://www.youtube.com/watch?v=tlaJf0CHbFE
 + https://www.youtube.com/watch?v=zc0ayq-c0OM
 + https://github.com/rstudio/webinars/blob/master/31-Web-APIs/01-APIs.pdf


## Thank you!
