---
title: "Data607 Project 2C"
author: "Deepa"
date: "3/13/2022"
output: html_document
---

### This dataset was share by Deepa Sharma for Superhero TV shows


1. Data: This is a Kaggle data from superhero TV shows

https://www.kaggle.com/anoopkumarraut/superhero-tv-shows/data

2. Possible Analysis:

 -  What is the highest-rated TV show of all times.
 -  What is the highest rated TV show from each year in the data set.

#### Import Library

```{r}
library(tidyverse)
library(readr)
library(curl)
##install.packages("curl")
library(ggplot2)
##install.packages("ggmap")
library(dplyr)
library(stringr)
library("magrittr")
```


#### Load data from Github (csv) into R dataframe

```{r}
df<- read.csv("https://raw.githubusercontent.com/deepasharma06/Data-607/main/Dataset_Superhero-TV-Shows.csv")
head(df)
```

#### This is to pull the columns needed for analysis and remove unnecessary columns

```{r}
library(tidyr)
df<- df[, c("show_title", "imdb_rating", "release_year", "genre")]
head(df)
```

#### This is to truncate the first 4 characters of release_year to get the year instead of a range

```{r}
df$release_year <- substr(df$release_year,1,4)
head(df)
```

#### This code is to replace any rows in imdb_rating column with a value of 'Not_Rated' with NA

```{r}
df$imdb_rating[df$imdb_rating == 'Not-Rated'] = NA
head(df)
```

#### This code is to replace any rows in imdb_rating column with a value of Null with NA

```{r}
df$imdb_rating[df$imdb_rating == ''] = NA
head(df)
```

#### This code is to replace any rows in release_year column with a value of 'TBA' with NA

```{r}
df$release_year[df$release_year == 'TBA'] = NA
head(df)
```

#### This code is to replace all rows with NA

```{r}
df <- na.omit(df) 
head(df)
```

#### This code is to reorder the data in the decreasing order of imdb_rating column

```{r}
df1 <- df[order(df$imdb_rating, decreasing = TRUE), ] 
head(df1)
```

#### We can see from the above table that the TV show 'Avatar: The Last Airbender' is the highest rated show of all times with a rating of 9.3

#### The following code is to reorder the data in the decreasing order of imdb_rating column but also grouping the data by 

```{r}

df2 <- df %>%
  arrange(desc(imdb_rating)) %>%
  group_by(release_year) %>%
  slice(1:1) %>%
  arrange(desc(release_year))
head(df2)
```



The above table shows the highest rated TV show for each year.

#### Conlcusion:
Based on the analysis of data we have the following conclusion:
'Avatar: The Last Airbender' is the highest rated show of all times with a rating of 9.3
The top rated shows for each year is available in the table above.


#### Reference:
YouTube. (2021, August 6). R select top n highest values by group (example) | extract head | reduce, rbind, dplyr &amp; data.table. YouTube. Retrieved March 13, 2022, from https://www.youtube.com/watch?v=Vhb7cvfRB5k 























