---
title: "Data607Project 1"
author: "Deepa Sharma"
date: "2/25/2022"
output: html_document
---


In this project, you’re given a text file with chess tournament results where the information has some structure. Your 
job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) 
with the following information for all of the players:
Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents
For the first player, the information would be:
Gary Hua, ON, 6.0, 1794, 1605
1605 was calculated by using the pre-tournament opponents’ ratings of 1436, 1563, 1600, 1610, 1649, 1663, 1716, and 
dividing by the total number of games played.

## Load tidyverse library

```{r}
library(tidyverse)

```

## Load the chessGame.txt file
I loaded text file to my github account and R read line from github.

```{r}
chessGame <- read_lines("https://raw.githubusercontent.com/deepasharma06/Data-607/main/ChessGame.txt", skip=4)
head(chessGame)


```

## Extract players names


```{r}
pattern_names <- "(?<=\\| )[A-Za-z -]{6,}(?=\\|)"
names <- str_match_all(chessGame, pattern_names)
##names

names2 <- str_trim(names[seq(1, length(names), 3)],
                   side = c("both","left","right"))
##names2
head(names2)

```

## Extract player’s States

```{r}
pattern_states <- "[A-Z]{2}(?=\\s\\|)"

states <- str_match_all(chessGame,pattern_states)
##states
states2 <- str_trim(states[seq(2, length(states), 3)],
                   side = c("both","left","right"))
##states2

head(states2)

```

## Extract player’s Points

```{r}

pattern_points <- "\\d\\.\\d"
points <- str_match_all(chessGame,pattern_points)
points2 <- str_trim(points[seq(1, length(points), 3)],
                    side = c("both","left","right"))
head(points2)

```

## Extract Players Rating

```{r}

## Pattern Rating

pattern_rating <- "((?<=R: )|(?<=R:  ))\\d{3,4}"
rating <- str_match_all(chessGame,pattern_rating)
#Remove unneeded rows
rating2 <- rating[seq(2, length(rating), 3)]

#Remove unneeded columns
rating_temp <- lapply(rating2, function(x) x[,-2])

# This to handle the Unrated people
rating_temp[lengths(rating_temp) == 0] <- "0000"

# Trim whitespace
rating2 <- str_trim(rating_temp,side = c("both","left","right"))

# Convert from character to numeric
rating2 <- unlist(lapply(rating2,as.numeric), recursive = FALSE)
head(rating2)

```

## Extract Players Played

```{r}
# This line extract every 3rd row
MychessGame <- chessGame[seq(1, length(chessGame), 3)]

# This pattern extracts the number that followed a D, W or L"
pattern_games <- "(((?<=W )|(?<=L ))|(?<=D ))\\s{0,3}\\d{0,2}(?=\\|)"

# Results are stored in this list of lists
players_played <- str_match_all(MychessGame,pattern_games)

# Lets remove 2 and 3 column, since I won't use them
players2 <- lapply(players_played, function(x) x[,-c(2:3)])

# Need to trim for whitespace
players2 <- lapply(players2,str_trim)
head(players2)

```


## Average


```{r}
index_players <- lapply(players2,as.numeric)
rows_players <- length(index_players)
player_opponents <- vector(mode = "list", length = rows_players)

for (row in 1:rows_players) {
  for (col in 1:length(index_players[[row]])) {
    player_opponents[[row]][col] <- rating2[[index_players[[row]][col]]]
  }
}

# Take mean first and then simplify list of vectors into a single vector
avg_players <- round(unlist(lapply(player_opponents,mean),recursive=FALSE))

head(avg_players)



```


## Create CSV file

```{r}
Result<- cbind(names2, states2, points2, rating2, avg_players)
write.csv(Result,"607project1.txt", row.names=FALSE)
##output
head(Result)

```

## check the CSV file

```{r}
check_csv_file <- read.csv("607project1.txt")
head(check_csv_file)
```

## Reference:
Youtube link:https://www.youtube.com/watch?v=uJKpz9T7mAg&t=469s

https://regexone.com/


```{r}

```

